A generalized model for the charge transport properties of dressed quantum Hall systems

### 2021-11-18 response/response.tex

Thank you very much for your effort in managing the review process of our manuscript. We are also thankful for the reviewer comments, and believe the second version of the manuscript we submit herewith has been significantly improved by the constructive criticism we received. Additionally, the subsequent sections of this document discuss the reviewer comments and our responses to them.

Please note that in the following sections, the statements in {\color{RoyalBlue} \textbf{blue}} are the comments of the reviewers. Our responses are shown in black letters, and the modifications we have done to the manuscript are given in {\color{Red} red}.

\subsection*{General changes to the manuscript}

We have made minor changes in language and presentation to improve clarity, and to match the rest of the manuscript better to the changes done to address the reviewers' comments.
\begin{itemize}
    \item Section I - seventh paragraph (page 2): \\
        {\color{Red} In Sec. VII, we discuss the physical significance of our theoretical results and their possible employments in future nanoelectronic devices.
        Finally, we summarize our findings and present our conclusions in Sec. VIII.}
    \item Section VI - fourth paragraph (page 8): \\
        {\color{Red} Considering the effects of the applied dressing field on the longitudinal conductivity of 2DEG, we can identify that the dressing field has sharpened the conductivity peaks.}
    \item Section VIII - first paragraph (page 10): \\
        {\color{Red} Finally, we derived analytical expressions for the diagonal components of electric conductivity tensor concerning the 2DEG quantum Hall system under low temperatures.}
\end{itemize}

@@

\subsection*{Response to the comments of Reviewer 1}

We would like to thank the reviewer for bringing the deficiencies of our manuscript to our attention and providing constructive feedback to improve the quality of our work. We have considered all of your suggestions seriously and revised our manuscript as described below.

\subsubsection*{Comment 1 -
\color{RoyalBlue} My concern is that the manuscript is heavily skewed towards a purely mathematical formulation of the problem. It has a minimal connection to realistic two-dimensional electron systems. The manuscript does not discuss how the results can be applied to understanding mechanisms of charge transport in nanoelectronic devices and can be used to optimize device performance. Without such discussion, the manuscript will have a minimal impact on the community working on developing nanoelectronics.}

We agree that our work has a theoretical bias, and the reader may benefit from some application perspective from our theoretical results to characterize or design nanoelectronic devices. Therefore, we have discussed the physical significance of our theoretical results and their possible use in optimizing nanoelectronic device performance. First, we added a detailed comparison between our theoretical results and experiment observation when no radiation is present.  We also added a new section (Section VII) on this very aspect.
,

\begin{itemize}
  \item Section VI - third paragraph (page 8):\\
  {\color{Red}
  By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems when no radiation is present against our results, we can identify that longitudinal conductivity oscillations in Fig. 4 are a repetition of the Shubnikov–de Haas(SdH) oscillations.
  As observed in the experimental work of Caviglia \textit{et al.} \cite{caviglia10}, the SdH oscillations period depends only on the perpendicular component of the magnetic field to the plane of the 2DEG.
  Therefore, we can identify that many experiments done in low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} have analyzed these SdH oscillations against the applied magnetic field amplitude for different types of 2DEGs.
  The cyclotron frequency ($\omega_0$) of the system depends on the magnetic field's perpendicular component to the plane of the 2DEG.
  Therefore we can achieve the same oscillatory behavior for longitudinal conductivity in 2DEG quantum Hall system by changing the gate voltage.
  The applied gate voltage to the system modifies the Fermi level of the system.
  Since the Landau level energy is only dependent on the cyclotron frequency, this gate voltage chnages generates SdH oscillations.
  This oscillatory behavior with applied gate voltage has been observed in an  experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
  By comparing these observations with our results in Fig. 4, we can identify that our oscillations also show the same characteristic behavior; i.e  $\hbar\omega_0$ periodic SdH oscillations against the Fermi energy.
  Furthermore, when we increase the gate voltage, the Fermi level rises. As illustrated in Fig. 4, this will result in a higher conductivity peak value at the higher-order Landau levels. This same behavior was also observed in the experimental observations presented in Ref. \cite{wakabayashi78}.
  In our work, we provide analytical results describing the controllability of these conductivity regions using a dressing field.
  }
  \item Section VII (page 9):\\
  {\color{Red}
  \subsection*{VII. PHYSICAL SIGNIFICANCE OF THE OUTCOMES}

  With the realization of 2DEGs in Si-MOSFETs (Metal Oxide Semiconductor Field Effect Transistors) \citep{fowler66}, Klitzing \textit{et al.} \cite{klitzing80} made the first transport measurements on such systems to reveal the quantum Hall effect. The empirical discovery of these unusual properties marked the beginning of a whole new realm in condensed matter physics that continues to produce phenomenal advancements in electronic systems. The quantum Hall effects in a 2DEG under a static magnetic field are described by plateaus quantized to integer values of the conductivity quantum ($\flatfrac{e^2}{\hbar}$) in the off-diagonal conductivity, with simultaneously peaks at inter-plateau transition for the diagonal conductivity \cite{endo09}. This is due to the applied magnetic field and it changes the energy spectrum of 2DEG dramatically. The magnetic field causes the density of states in 2DEG to split up into a sequence of delta functions, separated by an energy $\hbar\omega_0$, with $\omega_0$ the cyclotron frequency which depends on the applied magnetic field.
  However, experimental results demonstrate that these Landau levels are broadened and the main source of these broadening in low-temperatures is the disorders in materials \cite{ando85,dial07}. The broaden sequence of delta functions of density of states implies the oscillating behavior in the experimental measurements of longitudinal conductivity which is known as SdH oscillations. \cite{endo09,wakabayashi78}.

  Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system developed by considering low-temperature limit with gaussian impurity broadening assumptions.
  As illustrated in Fig. 4, we can describe the experimentally observed SdH oscillation results in Refs.\cite{endo09,wakabayashi78} through our model.
  Under the undressed condition, our results overlap with the conductivity measurement of quantum Hall systems \cite{endo09}. Strikingly, we show in Fig. 5 that we can manipulate the broadening of these conductivity peaks using an external dressing field. In low-temperatures, the principal cause of broadening of these conductivity peaks is impurity scattering and using an external dressing field we can suppress the scattering which results in shrinkage of both the scattering-induced broadening and the longitudinal conductivity peaks.

  Research on novel states of matter has driven the evolution of present-day nanoelectronic devices. In particular, controllable manipulation of material properties through a gate electric field has revolutionized the development of material science and technology \cite{ahn03,deng18}.
  The charge carrier concentration of a system is an imperative parameter that defines its conductivity properties.
  As we can manipulate the charge carrier concentration using an electrostatic field-effect, we exert significant control over the conductivity externally.
  A 2DEG under static magnetic field with quantum Hall effects is an excellent example that illustrates how the gate electric field controls conductivity.
  We also observed that a considerable number of studies exists on charge transport in the quantum limit that employed different types of 2D field-effect transistors (FETs) in magnetic fields \cite{wakabayashi78,yang18,long20,li14}. Yang \textit{et al.} \cite{yang18} study shows quantized Hall plateaus and SdH oscillations for longitudinal conductivity against gate voltage in black phosphorus FET under static magnetic fields in low-temperatures. Since the Fermi level of a system can be altered with the applied gate voltage, our Fig. 4 depicts this result.
  In particular, our analysisshoes that we can manipulate the broadening of the conductivity regions using an external dressing field. Although Yang \textit{et al.} \cite{yang18}, achieved broadening in longitudinal conductivity peaks by changing the temperature in a low range, in this study we presented a general theory on manipulating longitudinal conductivity broadening using a high-intensity electromagnetic field.

  The realization of the underlying mechanism of 2D FETs in the quantum realm promises its potential in next-generation nanoelectronic applications. In a particular application that uses the switching mechanism of the above-discussed FETs with quantum Hall effects, we can achieve high and low output conductivities by changing the input gate voltage. As a result of manipulating the broadening of conductivity regions, we can limit the broadening of conductivity peaks around Landau levels using a dressing high-intensity electromagnetic field. This will enhance the sensitivity of FETs which provides the ability to observe narrow changes in gate voltage.
  Furthermore, adopting the mechanism presented in Ref. \cite{hirakawa01}, we can manipulate conductivity peaks into very sensitive, narrowband high-frequency radiation detectors.
  We envision these advances in nanoelectronics from our theoretical model and knowledge generated from the insight it provides to the underlying dependencies.
  Furthermore, this theoretical model will aid for development of simulation tools that will design the quantum effects in magnetotransport properties of 2D nanostructures.
  }
\end{itemize}

### 2021-11-18 response/response.tex

  The realization of the underlying mechanism of 2D FETs in the quantum realm promises its potential in next-generation nanoelectronic applications. In a particular application that uses the switching mechanism of the above-discussed FETs with quantum Hall effects, we can achieve high and low output conductivities by changing the input gate voltage. As a result of manipulating the broadening of conductivity regions, we can limit the broadening of conductivity peaks around Landau levels using a dressing high-intensity electromagnetic field. This will enhance the sensitivity of FETs which provides the ability to observe narrow changes in gate voltage.
  Furthermore, adopting the mechanism presented in Ref. \cite{hirakawa01}, we can manipulate conductivity peaks into very sensitive, narrowband high-frequency radiation detectors.
  We envision these advances in nanoelectronics from our theoretical model and knowledge generated from the insight it provides to the underlying dependencies.
  Furthermore, this theoretical model will aid for development of simulation tools that will design the quantum effects in magnetotransport properties of 2D nanostructures.
  }
\end{itemize}

\subsubsection*{Comment 2 -
\color{RoyalBlue} Moreover, this current research direction has a significant overlap with previous experimental and theoretical studies of quantum Hall systems that started with the observation of zero-resistance states in high mobility systems [Zudov et al, Phys. Rev. B 64, 201311 (2001), Mani et al, Phys. Rev. Lett. 92, 146801 (2004)] and gave rise to theoretical models for the phenomenon [Durst et al, Phys. Rev. Lett. 91, 086803 (2003), Dmitriev et al., Phys. Rev. B 71, 115316 (2005), Dmitriev et al, Phys. Rev. B 80, 165327 (2009)]. The present manuscript needs to connect to various known phenomena discussed earlier in the literature on quantum Hall systems.}

We agree with the reviewer that it is useful to have a discussion comparing  our theoretical model and previous work on transport properties of quantum Hall systems.
Among the mentioned studies we can identify that experimental work reported in Refs. \cite{zudov01,mani02,zudov03,mani04} are specifically aimed at the unusual oscillations of the magnetoresistance induced by the microwave (millimeter-wave) radiation in 2DEG quantum Hall systems.

@@

These oscillations are known as \textit{microwave-induced resistance oscillations} (MIROs).
To describe these behaviors Durst \textit{et al.} \cite{durst03} introduced a simple theoretical model assuming that the experimentally observed oscillations are a consequence of photoexcited disorder-scattered electrons.
However, later a novel model was proposed in Refs. \cite{dmitriev03,dmitriev05,dmitriev09} considering the changes of the electron distribution function done by the microwave field.
These more generalized models \cite{dmitriev03,dmitriev05,dmitriev09} have successfully described the behavior of MIROs at experimentally relevant temperatures that were missed in the previous model \cite{durst03}.
Furthermore, we can recognize that the underlying mechanism of all these models \cite{durst03,dmitriev03,dmitriev05,dmitriev09} is microwave photon absorption by an electron in the associated system. In our theoretical model, we take into account higher frequencies than microwaves as the dressing field.
Therefore we can identify and quantify significant dissimilarities between our system and MIROs systems \cite{zudov01,mani02,zudov03,mani04,durst03,dmitriev03,dmitriev05,dmitriev09}. They are:

@@

\begin{itemize}
  \item
  in the experiments on magnetoresistance oscillations on 2DEG quantum Hall systems \cite{zudov01,mani02,zudov03,mani04} were performed in the microwave frequency range ($30 -\SI{150}{\giga\hertz}$). This leads to building the theoretical models presented in Refs. \cite{durst03,dmitriev03} by assuming that these oscillations are caused by photoexcited electrons. Since these models consider on relevant frequency range (microwave radiation), it will allow us to acknowledge the photon absorption by electrons. In contrast to that, our consideration is only focused on the systems with high-frequency range dressing fields which will not be associated with any photon absorption.

### 2021-11-18 paper/dressed_quantum_hall_response/dressed_quantum_hall_res.tex
Update response paper until sec.Vi

In contrast, we can observe more exciting phenomena by simultaneously applying a dressing field to a quantum Hall system already under a non-oscillating magnetic field.
Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, these studies  have not been utilized to describe the optical manipulation of charge transport.
{\color{Red}Recently, experimental research on the effects of microwave illumination of 2DEG systems revealed microwave-induced resistance oscillations (MIRO) under weak magnetic fields \cite{zudov01,mani02,zudov03,mani04}.
This inspired investigations on theoretical description of MIROs, and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}. These analytical formalisms provide a proper explanation for the experimental observations of MIROs. However, these experimental and theoretical works have been linked to photon absorption from low-frequency (microwave) fields.
In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system needs to be studied as a purely dressing (nonabsorbable) field.
The impacts induced by a purely dressing field on magnetotransport properties of 2DEG quantum Hall system need to be described by a non absorption mechanism and it has escaped the researchers’ attention before.
Lately, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall system under high-frequency field.} However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system.
{\color{Red}The authors of Ref.\cite{dini16} used the conductivity models from Refs. \cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening against Fermi level for each Landau level and provide less agreement with the empirical results.}

In the present analysis, we introduce a robust mathematical model for a dressed two-dimensional electron gas (2DEG) subject to another nonoscillating magnetic field.
A stationary magnetic field is applied perpendicularly across the surface of the 2DEG system. This causes the orbital motion of the electrons to be quantized, and a discrete energy spectrum with Landau splitting is observed \cite{landau30}.
{\color{Red}
It is important to note that, in this analysis, we consider the applied magnetic field at a range where the Anderson localization, the formation of the edge states, the spin splitting, and the electron-electron interactions can be neglected. The use of this assumption can also be found in the study done by Endo \textit{et al.} \cite{endo09}.
} In this study, we explicitly calculate the longitudinal components ($\sigma^{xx},\sigma^{yy}$) of the conductivity tensor in a periodically driven quantum Hall system by developing a generalized analytical description using the Floquet-Drude conductivity \cite{wackerl20}.
Finally, we demonstrate that our generalized model reproduces the results of the state-of-the-art conductivity model in Ref. \cite{endo09}, which was developed for the more specific case of quantum Hall systems without the external dressing field.
Moreover, we find that the optical field can be used as a mechanism to regulate transport behavior in numerous 2D nanostructures which can serve as a basis for many useful nanoelectronic devices. We believe that our theoretical analysis and visual depictions of numerical results will lead to a better understanding of manipulating charge transport. Moreover, this will inspire advanced  developments in nanoscale quantum devices.

@@

Symmetry conditions often give useful insights into the behaviors of physical quantum systems.
For instance, the famous Bloch analysis of electrons in quantum systems introduces a mathematical explanation for quantum systems occupying a discrete translational symmetry in the configuration space. Similarly, Floquet theory gives a mathematical formalism that can be used for translational symmetry in time rather than in space \cite{floquet83,grifoni98,holthaus15}.
The Floquet-Drude conductivity theory was employed recently by Wackerl \textit{et al.} \cite{wackerl20} as a method to analyze the transport properties of quantum systems exposed to strong radiation.
{\color{Red}In their study \cite{wackerl20}, the authors have presented more accurate results than the former theoretical descriptions \cite{morina15,pervishko15} for the conductivity of nanoscale systems in the  presence of a dressing field.} Therefore, we apply the Floquet-Drude conductivity theory to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.

@@

The Floquet-Fermi golden rule was proposed in Ref. \cite{wackerl20} as an approach to analyze the transport properties of dressed quantum systems with impurities.
However, this theory has not been applied for a dressed quantum Hall system in the previous studies. In this analysis, we use Floquet-Fermi golden rule to identify the effects induced by impurities on the magneto-transport properties.
With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and applying Floquet states derived in Eq.~(\ref{eq:14}), we can derive an  expression for $(l,l')$-th element of the inverse scattering time matrix for the $N$-th Landau level as
\begin{widetext}
\begin{equation} \label{eq:15}
  \begin{aligned}
    \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{ll'}_N = &
    \frac{ \pi \hbar\varrho^2}{e^2B^2} \delta(\varepsilon - \varepsilon_N) \\
    & \times
    \int_{-\infty}^{\infty}
    J_l \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
    J_{l'} \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
    \left|
    \int_{-\infty}^{\infty}
    \chi_N \left( \frac{\hbar}{eB}k_2 \right)
    \chi_N \bm{\left(} \frac{\hbar}{eB}
    \left( k_1 - {k}_x - k_2 \right) \bm{\right)}
    dk_2 \right|^2 d k_1,
  \end{aligned}
\end{equation}
\end{widetext}
where $\varrho = \eta_{imp} L_x \left[\flatfrac{ V_{imp}}{\pi}\right]^{1/2}$, $\varepsilon$ is a given energy value, $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, and $\varepsilon_N$ is the energy of the $N$-th Landau level.
A more detailed derivation is given in Appendix \ref{appendix_c}.
{\color{Red}
We modeled the effect caused by impurities in the considered system as a single short-range perturbation potential. Analyzing the electric properties for a specific impurity configuration is a rather formidable task and is not examined in this work since it is unlikely to have exactly the evaluated impurity configuration in an experiment.
Therefore, in this study, we consider the statistically averaged properties of 2DEG over impurity configurations.
Furthermore, we assumed that our perturbation potential is formed by a group of randomly distributed impurities under the Edwards impurity model \cite{akkermans10,wackerl20}.
Thus, we represented the total scattering potential in the 2DEG as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$. Then we  approximate the impurity potential into a Gaussian white noise \cite{akkermans10,wackerl20}.
Here $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
Moreover, in this analysis, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder. In this derivation, we only considered the first order (the Born approximation) contribution from the impurity potential.
}

@@

Next, we calculated the normalized energy band broadening against $x$-directional momentum component ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) for GaAs-based quantum well and the results are depicted in Fig.~\ref{fig:2} and Fig.~\ref{fig:3}. To make a comparison, we have selected the experiment parameters to match with analysis in Ref.~\cite{endo09}.
{\color{Red}In the study presented in Ref.~\cite{endo09}, the authors have assumed that the effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}.} In addition, they used the broadening of the undressed $0$-th Landau level $\Gamma_0$ as $\SI{0.24}{\milli\eV}$. Therefore, in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = \SI{0.24}{\milli\eV}$.
Here, we observe that the normalized energy broadening value for each Landau level is independent of the $x$-directional momentum $k_x$ value and we are able to manipulate it by the dressing field. When the dressing field's intensity increases, the energy broadening is reduced, which leads to changes in the transport properties of the dressed quantum Hall system.
To analyze these adjustments in detail, we derive an analytical expression for the conductivity of a dressed quantum Hall system in the next section.
%===============================================================================

@@

Since we consider the dressed quantum Hall system under the off-resonant condition, the absorption of photons are avoided. Therefore, we select the Fermi-Dirac distribution as our partial distribution function ($f$) for our system

@@

where $k_B$ is the Boltzmann constant, $T$ is the absolute temperature and $\varepsilon_F$ is the Fermi energy of the system. Under the low-temperature conditions ($k_BT \ll \varepsilon_F$), we can assume that the derivative of the Fermi-Dirac distribution is sharply peaked around the Fermi energy. This can be represented by the delta function \cite{endo09}

>>>>

In contrast, we can observe more exciting phenomena by simultaneously applying a dressing field to a quantum Hall system already under a non-oscillating magnetic field.
Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, these studies  have not been utilized to describe the optical manipulation of charge transport.
{\color{Red}
Recently, experimental research on the effects of microwave illumination of 2DEG systems revealed microwave-induced resistance oscillations (MIRO) under weak magnetic fields \cite{zudov01,mani02,zudov03,mani04}.
This inspired investigations on the theoretical description of MIROs, and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}. These formalisms provide a proper explanation for the experimental observations of MIROs. However, these experimental and theoretical works have been linked to photon absorption from low-frequency (microwave) fields.
In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system needs to be studied as a pure dressing (nonabsorbable) field.
The influence of induced by a pure dressing field on
magneto-transport properties of 2DEG quantum Hall system needs to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.
Lately, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall system subjected to a high-frequency field.}
However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system.
{\color{Red}
The authors of Ref. \cite{dini16} used the conductivity models from Refs. \cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening against Fermi level for each Landau level and provide less agreement with the empirical results.}

In the present analysis, we introduce a robust mathematical model for a dressed two-dimensional electron gas (2DEG) subject to another nonoscillating magnetic field.
A stationary magnetic field is applied perpendicularly across the surface of the 2DEG system. This causes the orbital motion of the electrons to be quantized, and a discrete energy spectrum with Landau splitting is observed \cite{landau30}.
{\color{Red}
It is important to note that, we limit the applied magnetic field to a range where we can neglect effects such as Anderson localization, formation of the edge states, spin splitting, the electron-electron interactions. This is not an overly restrictive assumption and others have used the same assumption in their work, e.g. see \textit{et al.} \cite{endo09}.
} In this study, we explicitly calculate the longitudinal components ($\sigma^{xx},\sigma^{yy}$) of the conductivity tensor in a periodically driven quantum Hall system by developing a generalized analytical description using the Floquet-Drude conductivity \cite{wackerl20}.
Finally, we demonstrate that our generalized model reproduces the results of the state-of-the-art conductivity model in Ref. \cite{endo09}, which was developed for the more specific case of quantum Hall systems without the external dressing field.
Moreover, we find that the optical field can be used as a mechanism to regulate transport behavior in numerous 2D nanostructures which can serve as a basis for many useful nanoelectronic devices. We believe that our theoretical analysis and visual depictions of numerical results will lead to a better understanding of manipulating charge transport. Moreover, this will inspire advanced  developments in nanoscale quantum devices.

@@

Symmetry conditions often give useful insights into the behaviors of physical quantum systems.
For instance, the famous Bloch analysis of electrons in quantum systems introduces a mathematical explanation for quantum systems occupying a discrete translational symmetry in the configuration space. Similarly, Floquet theory gives a mathematical formalism that can be used for translational symmetry in time rather than in space \cite{floquet83,grifoni98,holthaus15}.
The Floquet-Drude conductivity theory was employed recently by Wackerl \textit{et al.} \cite{wackerl20} as a method to analyze the transport properties of quantum systems exposed to strong radiation.
{\color{Red}
In their study \cite{wackerl20}, the authors have presented more accurate results than the former theoretical descriptions \cite{morina15,pervishko15} for the conductivity of nanoscale systems in the  presence of a dressing field.} Therefore, we apply the Floquet-Drude conductivity theory to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.

@@

The Floquet-Fermi golden rule was proposed in Ref. \cite{wackerl20} as an approach to analyze the transport properties of dressed quantum systems with impurities.
However, this theory has not been applied for a dressed quantum Hall system in the previous studies. In this analysis, we use Floquet-Fermi golden rule to identify the effects induced by impurities on the magneto-transport properties.
With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and applying Floquet states derived in Eq.~(\ref{eq:14}), we can derive an  expression for $(l,l')$-th element of the inverse scattering time matrix for the $N$-th Landau level as
\begin{widetext}
\begin{equation} \label{eq:15}
  \begin{aligned}
    \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{ll'}_N = &
    \frac{ \pi \hbar\varrho^2}{e^2B^2} \delta(\varepsilon - \varepsilon_N) \\
    & \times
    \int_{-\infty}^{\infty}
    J_l \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
    J_{l'} \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
    \left|
    \int_{-\infty}^{\infty}
    \chi_N \left( \frac{\hbar}{eB}k_2 \right)
    \chi_N \bm{\left(} \frac{\hbar}{eB}
    \left( k_1 - {k}_x - k_2 \right) \bm{\right)}
    dk_2 \right|^2 d k_1,
  \end{aligned}
\end{equation}
\end{widetext}
where $\varrho = \eta_{imp} L_x \left[\flatfrac{ V_{imp}}{\pi}\right]^{1/2}$, $\varepsilon$ is a given energy value, $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, and $\varepsilon_N$ is the energy of the $N$-th Landau level.
A more detailed derivation is given in Appendix \ref{appendix_c}.
{\color{Red}
We have modeled the effect caused by impurities as a single short-range perturbation potential. Analyzing the electric properties for a specific impurity distribution is a rather formidable task. We do not consider a specific impurity distribution here as it is unlikely to represent a measured impurity configuration in an experiment.
Therefore, in this study, we consider the statistically averaged properties of 2DEG over impurity configurations.
Furthermore, we have assumed that a group of randomly distributed impurities forms our perturbation potential under the Edwards impurity model  \cite{akkermans10,wackerl20}.
Essentially, all these assumptions mean that we can write the total scattering potential in the 2DEG as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$. This enables us to approximate the impurity potential as a Gaussian white noise \cite{akkermans10,wackerl20},
where $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
Moreover, in this analysis, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder. In this derivation, we only considered the first order (the Born approximation) contribution from the impurity potential.
}

@@

Next, we calculated the normalized energy band broadening against $x$-directional momentum component ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) for GaAs-based quantum well and the results are depicted in Fig.~\ref{fig:2} and Fig.~\ref{fig:3}. To make a comparison, we have selected the experiment parameters to match with analysis in Ref.~\cite{endo09}.
{\color{Red}In the study presented in Ref. \cite{endo09}, the authors have assumed that the effective mass of an electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}.} In addition, they used the broadening of the undressed $0$-th Landau level $\Gamma_0$ as $\SI{0.24}{\milli\eV}$. Therefore, in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = \SI{0.24}{\milli\eV}$.
Here, we observe that the normalized energy broadening value for each Landau level is independent of the $x$-directional momentum $k_x$ value and we are able to manipulate it by the dressing field. When the dressing field's intensity increases, the energy broadening is reduced, which leads to changes in the transport properties of the dressed quantum Hall system.
To analyze these adjustments in detail, we derive an analytical expression for the conductivity of a dressed quantum Hall system in the next section.
%===============================================================================

@@

We consider a dressed quantum Hall system under off-resonant condition, where photon absorption does not happen. Therefore, we can select the Fermi-Dirac distribution as our partial distribution function ($f$) for our system

@@

where $k_B$ is the Boltzmann constant, $T$ is the absolute temperature, and $\varepsilon_F$ is the Fermi energy of the system. At low-temperatures, i.e., $k_BT \ll \varepsilon_F$, the derivative of this distribution is sharply peaked around the Fermi energy, and can be approximated by a delta function
